Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-25 fmics/paper.tex
start formatting statement of one of the main theorems

The formal definitions of the functions listed in Table~\ref{tab:descriptions} are given in Figure~\ref{fig:definitions}.
Note that the definition of $\mathsf{input}$ when $n=0$ or when $n>6$ does not change the structure presented.
A similar comment applies to other definitions when $n$, representing a slice number, is $0$, or when $x$, representing a shift register position, is greater than $1$.
Every definition in Figure~\ref{fig:definitions} is \emph{local} (only represents a small part of the SRS structure) and therefore the verification against its intended meaning is relatively straightforward.

@@

>>>>

The formal definitions of the functions listed in Table~\ref{tab:descriptions} are given in Figure~\ref{fig:definitions}.
Note that the definition of $\mathsf{input}$ when $n=0$ or when $n>6$ does not change the structure presented.
A similar comment applies to other definitions when $n$, representing a slice number, is $0$, or when $x$, representing a shift register position, is greater than $1$.
Every definition in Figure~\ref{fig:definitions} is \emph{local} (only represents a small part of the SRS structure) and therefore verification against its intended meaning is relatively straightforward.

@@

\begin{figure}
\caption{
Definitions of auxiliary HOL functions used while proving theorems about the model of the SRS structure.
\label{fig:auxdefs}
}
\begin{align*}
\mathsf{delay\_sum}\;0&=0\\
\mathsf{delay\_sum}\;n&=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\\
&\qquad\text{where $(n',\_)=\mathsf{input}\;n$}
\end{align*}
\begin{align*}
\mathsf{last\_update}\;n\;0&=0\\
\mathsf{last\_update}\;n\;t&=\text{if $\mathsf{update\_time}\;n\;t$ then $t$}\\
&\qquad\text{else }\mathsf{last\_update}\;n\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\end{figure}

\begin{multline*}
\forall{D\,n\,x\,t}.\,{0 < n}\land{\mathsf{update\_time\;n\;t}}\implies\\\mathsf{output}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)-1}\begin{cases}0&t<m+\mathsf{delay\_sum}\;n\\D\;(t-m-\mathsf{delay\_sum}\;n)&\text{otherwise}\end{cases}
\end{multline*}
